Automated Formal Synthesis\\ of Safe Digital Controllers for Continuous Plants

### 2019-01-08 automatica/paper.tex
fix
typo

We use $\mathcal{F}_{\langle E,M \rangle}(x)$ to denote a real number $x$
represented in a floating point domain, with $E$ bits representing the exponent
part and $M$ bits representing the mantissa part. 
In particular, we use $\mathcal{F}_{\langle E_c,M_c \rangle}(x)$ to denote a real number 
represented at the floating-point precision of the controller, and 
$\mathcal{F}_{\langle E_p,M_p \rangle}(x)$ to denote a real number 
represented at the fixed-point precision of the plant model.  \note{no assumptions on relative value btw controller and plant?}

@@

Regarding the second requirement, 
we fix an index $k$, 
and we synthesize a safe controller by
unfolding the transition system $k$ steps and by selecting a controller $K$ and a single initial state, 
such that the states at each step do not violate the safety criteria (see Section~\ref{ssec:safespecification}).    
That is, we ask the bounded model checker~\cite{ClarkeKL04} if there exists a $K$ that is safe for at least one $x_0$ in our set of all possible initial states, and a given fixed point precision for the controller, and where the input signal remains within the specified bounds.
This approach sound if the current $k$ is greater than the completeness threshold (see later step).  
We~also assume some (fixed or floating point) precision $\langle I_p,F_p\rangle$ for the plant and a sampling rate.  
The checks that these assumptions hold are performed by subsequent {\sc verify} stages.

@@

\item {\bf Overflow:}
The maximum size of a real number $x$ that can be represented in a fixed
point domain as $\mathcal{F}_{\langle I,F \rangle}(x)$ is $\pm
(2^{I-1}+1-2^{-F})$.  Numbers outside this range cannot be represented by
the domain.  We check that overflow does not occur \note{and if it does \ldots}.

>>>>

We use $\mathcal{F}_{\langle E,M \rangle}(x)$ to denote a real number $x$
represented in a floating point domain, with $E$ bits representing the exponent
part and $M$ bits representing the mantissa part. 
In particular, we use $\mathcal{F}_{\langle E_c,M_c \rangle}(x)$ to denote a real number 
represented at the floating-point precision of the controller, and 
$\mathcal{F}_{\langle E_p,M_p \rangle}(x)$ to denote a real number 
represented at the fixed-point precision of the plant model.

@@

Regarding the second requirement, 
we fix an index $k$, 
and we synthesize a safe controller by
unfolding the transition system $k$ steps and by selecting a controller $K$ and a single initial state, 
such that the states at each step do not violate the safety criteria (see Section~\ref{ssec:safespecification}).    
That is, we ask the bounded model checker~\cite{ClarkeKL04} if there exists a $K$ that is safe for at least one $x_0$ in our set of all possible initial states, and a given fixed point precision for the controller, and where the input signal remains within the specified bounds.
This approach is sound if the current $k$ is greater than the completeness threshold (see later step).  
We~also assume some (fixed or floating point) precision $\langle I_p,F_p\rangle$ for the plant and a sampling rate.  
The checks that these assumptions hold are performed by subsequent {\sc verify} stages.

@@

\item {\bf Overflow:}
The maximum size of a real number $x$ that can be represented in a fixed
point domain as $\mathcal{F}_{\langle I,F \rangle}(x)$ is $\pm
(2^{I-1}+1-2^{-F})$.  Numbers outside this range cannot be represented by
the domain.  If overflow occurs, the interval bound becomes infinite.
